Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-04 manuscript/manuscript.Rmd
figure brainstorm

# Section title {#sec:1}

Text with citations by \cite{Galyardt14mmm}.

## Subsection title {#sec:2}

as required. Don't forget to give each section
and subsection a unique label (see Sect. \ref{sec:1}).

#### Paragraph headings

Use paragraph headings as needed.

\begin{align}
a^2+b^2=c^2
\end{align}

>>>>

# Figures brainstorm

Figure 1: 1-D and 3-D model conceptual figure. something about the objective / decision
Figure 2: Stability / multistability in the 1D and 3D models.  state space + time views

Figure 3: The 1-D optimal management solution.  'constant escapement' intuition etc

Results figures:
- timeseries example of management under the RL policy.  probably compare to managing under 1-D solution / rule-of-thumb methods
- state-space view of management doughnut 
- visualization / encapsulation of the policy heatmaps, slices, policy vs position along ellipse 
- reward plot over time (comparing methods)
